---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gest

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/alexhallam/gest.svg?branch=master)](https://travis-ci.org/alexhallam/gest)
<!-- badges: end -->

The goal of gest is to create shrinkage estimates in a flexible and fast way.
This package is a convenient wrapper for the `deconvolveR` package.
## Installation

You can install the released version of gest from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("gest")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("alexhallam/gest")
```
## Example

In the example below we use the `add_binom_gest` to calculate the "g-estimates" which
are shrinkage estimators. Full posterior distributions are also calculated along with
confidence intervals. 

```{r example}
library(tibble)
library(gest)
set.seed(2017)

# simulate 200 random examples from a beta-binomial
obs <- 200
dat <- tibble(prob = rbeta(obs, 10, 50),
                 n = round(rlnorm(obs, 4, 2)) + 1,
                 x = rbinom(obs, n, prob))
result <- add_binom_gest(dat, x, n)
result
```

# Related Work

[ebbr](https://github.com/dgrtwo/ebbr)

# Academic Work

[deconvolveR](https://cran.r-project.org/web/packages/deconvolveR/deconvolveR.pdf)
