---
title: "Baseball Binomial Shrinkage"
author: "Alex Hallam"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{baseball-binomial-shrinkage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette we will show how to use this package to shrink baseball averages. This is similar
to beta-binomail shrinkage, but with a more flexible prior. We use the same setup as shown in 
[David Robinson's Post](http://varianceexplained.org/r/empirical_bayes_baseball/).

### Data Prepation

We first prepare the data

```{r setup}
library(gest)
library(Lahman)
library(tidyverse)
career <- Batting %>%
  filter(AB > 0) %>%
  anti_join(Pitching, by = "playerID") %>%
  group_by(playerID) %>%
  summarize(H = sum(H), AB = sum(AB)) %>%
  mutate(average = H / AB)

# use names along with the player IDs
career <- Master %>%
  tbl_df() %>%
  select(playerID, nameFirst, nameLast) %>%
  unite(name, nameFirst, nameLast, sep = " ") %>%
  inner_join(career, by = "playerID") %>%
  select(-playerID)

head(career)
```

### Add posterior estimates

We are now in a position to add posterior estimates. You will note that this operation takes a few seconds.
This can be made faster by deceasing the grain of the parameter space (`theta_by`) which is set to 0.01 by
default.

```{r add_post}
df_augmented <- career %>% 
  mutate(x = H, n = AB) %>% 
  add_binom_gest()

head(df_augmented)
```

